---
title: "13: Why reactivity?"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(shiny)
```

## Interesante

> [40 years ago] I imagined a magic blackboard that if you erased one number and wrote a new thing in, all of the other numbers would automatically change, like word processing with numbers.

-- Dan Bricklin ([Ted talk](https://www.youtube.com/watch?v=YDvbDiJZpy0&feature=youtu.be))

## Desafio

Quiero una herramienta interactive y eficiente:

* Reactive expressions and outputs update if and only if their inputs change. 

* Outputs stay in sync with inputs, never doing more work than necessary.

## Implementacion ingenua

```{r}
valor <- 10
out <- function() {
  message("Corriendo") 
  valor * 100
}
```

```{r}
# Valor nuevo
valor <- 10
valor

# Corre?
out()

# Corre?
out()
out()

# Valor nuevo
valor <- 9

# Corre?
out()

# Corre?
valor <- 9
out()
out()
```

## Shiny

## Interesante 2

Falla.

```{r, error = TRUE}
call_reactive <- reactive(1)
call_reactive()
```

Funciona.

```{r, error = TRUE}
# shiny-devel
# remotes::install_github("rstudio/shiny")
reactiveConsole(TRUE)

call_reactive <- reactive(1)
call_reactive()
```

```{r, error = TRUE}
out <- reactive({
  message("Corriendo")
  valor() * 100
})
```

## Por que reactividad?

> Lazy: it doesn't do any work until it's called.

> Cached: it doesn't do any work the second and subsequent times it's called because it caches the previous result.

Ejemplo:

```{r}
# Valor nuevo
valor <- reactiveVal(10)
valor()

# Corre?
out()

# Corre?
out()
out()

# Valor nuevo
valor(9)

# Corre?
out()

# Corre?
valor(9)
out()
out()
```

