---
title: "13: Why reactivity?"
output: github_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(shiny)
```

## Interesante

> [40 years ago] I imagined a magic blackboard that if you erased one number and wrote a new thing in, all of the other numbers would automatically change, like word processing with numbers.

-- Dan Bricklin ([Ted talk](https://www.youtube.com/watch?v=YDvbDiJZpy0&feature=youtu.be))

## Desafio

Quiero una herramienta interactive y eficiente:

1. Si los inputs cambian, los outputs cambian.
2. Si los inputs no cambian, los outputs no cambian.
3. Si los inputs no cambian, y el output ya fue calculado, no recalcula.



# Implementacion ingenua

```{r}
output <- function() {
  message("Calculando") 
  input * 100
}
```

## 1. Si: Si los inputs cambian, los outputs cambian

```{r}
input <- 10
output()

input <- 9
output()
```

## 2. Si: Si los inputs no cambian, los outputs no cambian

```{r}
input <- 9
output()

input <- 9
output()
```

## 3. No: Si los inputs no cambian, y el output ya fue calculado, no recalcula

```{r}
input <- 9
output()

input <- 9
output()
```



# Interesante

Falla.

```{r, error = TRUE}
call_reactive <- reactive(1)
call_reactive()
```

Funciona.

```{r, error = TRUE}
# remotes::install_github("rstudio/shiny")
packageVersion("shiny")
reactiveConsole(TRUE)

call_reactive <- reactive(1)
call_reactive()
```



# Implementación con shiny

```{r, error = TRUE}
input <- reactiveVal(0)
input()
input(1)
input()

output <- reactive({
  message("Calculando")
  input() * 100
})

output()
```

## Si, Si, Si

```{r}
# 1. Si: Si los inputs cambian, los outputs cambian.
input(10)
output()
input(9)
output()

# 2. Si: los inputs no cambian, los outputs no cambian.
# 3. Si: Si los inputs no cambian, y el output ya fue calculado, no recalcula.
input(9)
output()
```

